A standardized framework for risk-based assessment of treatment effect heterogeneity in observational healthcare databases

### 2021-08-24 submission/manuscript.rmd
take notes in preparation for rebuttal text

***We aimed to develop a framework for implementing risk-based assessment of
treatment heterogeneity in high-dimensional observational data, extending the
existing guidelines of the RCT setting. Our contribution provides an
out-of-the-box solution for implementing such analyses at scale within the OHDSI
network, taking advantage of the OMOP-CDM.***

>>>>

***We aimed to develop a framework for implementing risk-based assessment of
treatment heterogeneity in high-dimensional observational data, extending the
existing guidelines of the RCT setting. Our publicly available package provides
an out-of-the-box solution for implementing such analyses at scale within the
OHDSI network, taking advantage of the OMOP-CDM.***
